\langname: A Language for Multi-View Architecture Description and Control

### 2017-08-12 paper.tex
Section 3

\lstdefinestyle{modulestyle}{
	basicstyle=\scriptsize
}

\lstdefinestyle{cncstyle}{
	aboveskip=0pt,
	belowskip=-10pt,
	basicstyle=\footnotesize\ttfamily,
	captionpos=b,
	columns=flexible,
	float=t,
	frame=single,
	morekeywords={component},
	keywordstyle=\color{blue},
	numbers=left,
	numberstyle=\color{gray}\scriptsize\fontfamily{cmr}\selectfont,
	numbersep=8pt,
	tabsize=2,
	xleftmargin=19pt,
	framexleftmargin=15pt,
	framexrightmargin=-4pt
}

\lstdefinelanguage{cnclang}{
	morekeywords={component, port},
}

\lstdefinestyle{allocationstyle}{
}

@@

@@

\begin{abstract}
This is the text of the abstract.
\end{abstract}

@@

Module view:

Component-and-connector view:

Deployment view:

\begin{lstlisting}[style=cncstyle, caption=Caption, label=cncview, language=cnclang]
component Test
	port port1
	port port2
\end{lstlisting}

\lstlistingname~\ref{cncview}

>>>>

\lstdefinestyle{modulestyle}{
	aboveskip=0pt,
	belowskip=-10pt,
	basicstyle=\footnotesize\ttfamily,
	captionpos=b,
	belowcaptionskip=0pt,
	columns=flexible,
	float=t,
	frame=single,
	keywordstyle=\color{blue},
	numbers=left,
	numberstyle=\color{gray}\scriptsize\fontfamily{cmr}\selectfont,
	numbersep=8pt,
	tabsize=2,
	xleftmargin=19pt,
	framexleftmargin=15pt,
	framexrightmargin=-4pt
}

\lstdefinelanguage{modulelang}{
	morekeywords={resource, type, def, module, val, var}
}

\lstdefinestyle{cncstyle}{
	aboveskip=0pt,
	belowskip=-10pt,
	basicstyle=\footnotesize\ttfamily,
	captionpos=b,
	belowcaptionskip=0pt,
	columns=flexible,
	float=t,
	frame=single,
	keywordstyle=\color{blue},
	numbers=left,
	numberstyle=\color{gray}\scriptsize\fontfamily{cmr}\selectfont,
	numbersep=8pt,
	tabsize=2,
	xleftmargin=19pt,
	framexleftmargin=15pt,
	framexrightmargin=-4pt
}

\lstdefinelanguage{cnclang}{
	morekeywords={component, port, connector, val, architecture, components, connectors, connections, connect, and, with, entryPoints}
}

\lstdefinestyle{allocationstyle}{
	aboveskip=0pt,
	belowskip=-10pt,
	basicstyle=\footnotesize\ttfamily,
	captionpos=b,
	belowcaptionskip=0pt,
	columns=flexible,
	float=t,
	frame=single,
	keywordstyle=\color{blue},
	numbers=left,
	numberstyle=\color{gray}\scriptsize\fontfamily{cmr}\selectfont,
	numbersep=8pt,
	tabsize=2,
	xleftmargin=19pt,
	framexleftmargin=15pt,
	framexrightmargin=-4pt
}

\lstdefinelanguage{allocationlang}{
	morekeywords={deployment, extends}
}

@@

% FIXME: Comment the following when you need to add copyright information.
\makeatletter
\def\@copyrightspace{\relax}
\makeatother

@@

%\begin{abstract}
%This is the text of the abstract.
%\end{abstract}

@@

\noindent
\\
\textit{\textbf{Module view.}} Module view is used to document the principal implementation units of a system, together with the relations among these units. The primary elements in module view are implementation units that provide a coherent set of responsibilities. In \langname, implementation units take the form of capability-based modules.

%Every module has a collection of properties associated with it. These properties are intended to express the important information associated with the module, as well as constraints on the module. Sample properties are responsibilities, visibility information, and author or owner.

Modules are related to one another using the depends on relation.

What is a module view useful for? The module view can be used to determine how a system's source code is decomposed into units, what assumptions each unit can make about services provided by other units, and how these units are aggregated into larger ensembles. The module view can thus be used to create an implementation plan and also to determine how changes to one part of a system might affect other parts and thus reason about the system's modifiability, portability and reuse.

\begin{lstlisting}[style=modulestyle, caption=Module view of a client/server system, label=moduleview, language=modulelang]
resource type CSIface
	def getVal(key: String): String

module def Client(cPlumbing: CSIface): ClientIface
	def startClient(): Unit
		...

module def Server(sPlumb: SPlumbing): ServerIface
	module def sendInfo(): CSIface
		def getVal(key: String): String
			...

	def startServer(): Unit
		sPlumb.setFn(sendInfo().getVal)
		...
\end{lstlisting}

\noindent
\\
\textit{\textbf{Component-and-connector view.}} Component-and-connector view expresses runtime behavior. It is described in terms of components and connectors. A component is one of the principal processing units of the executing system. Components might be services, processes, threads, filters, repositories, peers, or clients and servers, to name a few. A connector is the interaction mechanism among components. Connectors include pipes, queues, request/reply protocols, direct invocation, event-driven invocation, etc. Components and connectors can be decomposed into other components and connectors. The decomposition of a component may include connectors and vice versa.

\begin{lstlisting}[style=cncstyle, caption=C\&C view of the client/server system, label=cncview, language=cnclang]
component Client
	port getInfo: requires CSIface

component Server
	port sendInfo: provides CSIface

connector JSONCtr
	val host: IPAddress
	val prt: Int

architecture ClientServer
	components
		Client client
		Server server

	connectors
		JSONCtr jsonCtr

	connections
		connect client.getInfo and server.sendInfo
			with jsonCtr

	entryPoints
		client: startClient
		server: startServer
\end{lstlisting}

\noindent
\\
\textit{\textbf{Allocation view.}} Allocation view describes the mapping of software units to elements of an environment in which the software is developed or executes. The environment might be the hardware, the file systems supporting development or deployment, or the development organization(s).

\begin{lstlisting}[style=allocationstyle, caption=Allocation view of the client/server system, label=allocationview, language=allocationlang]
deployment CSDeployment extends ClientServer
	jsonCtr.host = 127.0.0.1
	jsonCtr.port = 9090
\end{lstlisting}

\begin{lstlisting}[style=modulestyle, caption=Plumbing code generated for the client, label=clientplumbing, language=modulelang]
module def cPlumbing(tcpClient: TCPClient): CSIface
	def getVal(key: String): String
		tcpClient.connect(IPAddress("127.0.0.1"), 9090)
		...

val tcpClient = TCPClient()
val plumbing = cPlumbing(tcpClient)
val c = client(plumbing)
c.start()
\end{lstlisting}

\lstlistingname~\ref{cncview}
\cite{Nistor2013} \cite{Melicher2017}
